SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-13 paper/bio.tex
my changes

>>>>

\input{pm-1-matrix}

\begin{example}
In figure~\ref{fig:M1}(a), we present a VTS that has three compartments as nodes, vesicles as edges,
and 8 molecules.
Each node and edge is labelled with a set of molecules that present in them.
Overline on a molecule indicates activation.
In figure~\ref{fig:M1}(b), we present the corresponding fusion matrix.
\ashu{discuss the properties on the figure.}
\end{example}

### 2017-07-13 paper/conclusion.tex
added
my changes

>>>>

In the experiments, we have demonstrated the power of SMT solvers and the value
of careful encoding of the problems into SMT queries.
%
We manage to scale the tool upto the size that interests biologists.
%
However, there are many further search problems are of interest to
biologists about the VTSs.
%
For example, are there any k-connected graphs that can not be
converted into a VTS?
%
This encoding induces a quantifier alternation in the problem.
%
Therefore, a simple quantifier free encoding will not work.
%
We are planning to use QBF solvers to solve such queries or develop
iterative search algorithm for such queries.
%

% \ankit{interpret experiments (3-4 lines)}

% \srivas{Future work(quantifier problem etc)}
